CS6999 Web Data and Text Mining:\\Parallel Text Indexer Project Report

### 2011-06-07 report/report.tex
First draft

Algorithm enhancements usually represent the forefront of research in
the field. Work to validate a new concept or algorithm is usually
performed in a very controlled environment and on relatively small
document collections. As the field matures, improvements are harder
fought and often involve increasingly complex algorithms and corpus
approximation methods into which it becomes more difficult to
\textit{fold-in} new documents. In addressing the considerable
computation cost of re-calculating \textit{LSI} \cite{RefWorks:102}
approximations, \cite{RefWorks:101} introduced new update methods
which saw improved average precisions but were forced to conclude that
the improvements were at a computational premium over previous
methods. A semi-discrete matrix decomposition for LSI, \textit{SDD},
performs as well as the original SVD-based LSI method for equal query
times and uses less storage \cite{RefWorks:99}. The decomposition time
of the new method, however, is significantly larger than the original.

@@

%----------------------------------------
% Research Plan
%----------------------------------------
\section{Research Plan}
\label{sec:researchplan}

The research design and methods section should include the following:

\begin{itemize}
    \item an overview of the experimental design

    \item a detailed description of specific methods to be employed to accomplish the specific aims

    \item a detailed discussion of the way in which the results will be collected, analyzed, and interpreted

    \item a projected sequence or timetable (work plan)

    \item a description of any new methodology used and why it represents an improvement over the existing ones

    \item a discussion of potential difficulties and limitations and how these will be overcome or mitigated

    \item expected results, and alternative approaches that will be used if unexpected results are found

    \item precautions to be exercised with respect to any procedures, situations, or materials that may be hazardous to personnel or human subjects
\end{itemize}

Suggestion:

    Number the sections in this part of the application to correspond to the numbers of the Specific Aims.

    Give sufficient detail. Do not assume that the reviewers will know how you intend to proceed.

    Avoid excessive experimental detail by referring to publications that describe the methods to be employed.

    Publications cited should be by the applicants, if at all possible. Citing someone else's publication establishes that you know what method to use, but citing your own (or that of a collaborator) establishes that the applicant personnel are experienced with the necessary techniques.

    If relevant, explain why one approach or method will be used in preference to others. This establishes that the alternatives were not simply overlooked. Give not only the "how" but the "why."

    If employing a complex technology for the fast time, take extra care to demonstrate familiarity with the experimental details and potential pitfalls. Add a coinvestigator or consultant experienced with the technology, if necessary.

    Document proposed collaborations and offers of materials or reagents of restricted availability with letters from the individuals involved.

@@

\begin{figure}
  \begin{center}
        \includegraphics[width=\textwidth,height=!]{overallclassdiagram}
  \end{center}
  \caption{Overall UML class diagram design}
  \label{fig:overallclassdiagram}
\end{figure}

@@

The indexer system maintains an \textit{inverted index} of an evolving
corpus and services concurrent search requests against the index. The
current implementation is based on boolean retrieval methods described
in \cite{RefWorks:109}. An Aho-Corasick state machine
\cite{RefWorks:103} is used to scan documents for a predefined set of
keywords, and construct a term index for each document (delta
index). The term occurrences for each document are used to augment an
existing index for documents already processed. The document
collection, index, and keyword list are maintained in a single MySQL
database instance. It is through this database that the parallel
indexer instances are initialized and synchronized. This configuration
is operationally simple and easy to implement but the database has the
potential to become a throttle point as the system is scaled to larger
and faster-evolving document collections, and is required to service a
higher rate of queries. In order to scale the current implementation
to large document collections, a more efficient mechanism would be
required in this respect.

@@

\begin{itemize}
\item \texttt{List<Document> getDocuments (int count)}: retrieve a
  specified number of unprocessed documents from the database. The
  documents retrieved will be atomically marked as processed so that
  processing is not duplicated on other nodes. In this scheme, a
  document is considered processed to all other processes once
  retrieved from the database. This may cause problems from a fault
  recovery perspective if the processing node fails. A proposed
  enhancement to this scheme is to use another state, processing, to
  indicate that the document has been retrieved and to update the
  state to a processed state once processing is actually complete. For
  the initial implementation we will use the processed state only.

@@

 Figures \ref{fig:indexclassdiagram} and
 \ref{fig:indexsequencediagram} shows the UML class and sequence
 diagrams respectively for classes and methods involved in the
 implementation of the Index data access layer.

@@

Figures \ref{fig:searcherclassdiagram} and
\ref{fig:searchersequencediagram} shows the UML class and sequence
diagrams respectively for classes and methods involved in the
implementation of the \texttt{Searcher} class.

@@

Figures \ref{fig:statemachineclassdiagram} and
\ref{fig:statemachinesequencediagram} shows the UML class and sequence
diagrams respectively for classes and methods involved in the
implementation of the \texttt{StateMachineBuilder}.

@@

Figures \ref{fig:parserclassdiagram} and
\ref{fig:parsersequencediagram} shows the UML class and sequence
diagrams respectively for classes and methods involved in the
implementation of the \texttt{Parser}.

@@

%----------------------------------------
% Experiment Results
%----------------------------------------
\section{Experiment Results}
\label{sec:experimentresults}
The whole idea of the project belongs in being able to reduce the time
to build the index. As our system is building the inverted index by
parsing all the post into the state machine, we can expect that the
complexity will be proportional to the whole number of characters of
all the post we want to build the index for. As a result changing the
number of Posts, the number of characters inside of each post should
have a big impact in our time complexity. Besides, we should also have
a time needed at the very beginning of the running to build the state
machine. We can expect that the building of the state machine needs a
time proportional to the sum of the size of the keywords.

The system proposed in this paper doesn’t take care of various
compression techniques for storing the index. To do that, many
techniques have been explored in the literature. We will just
highlight the different sizes of our indexes according to different
parameters.

Finally we will do a time comparison between our way of building the
inverted index and the naive way.  All the time complexities tests are
done on a single computer and it is important to understand that all
these processes can be parallelized. A future work would be to install
the system on multiple computers and explore the gain in time by
running the code simultaneously on these computers.

All tests were run on a single Intel Core 2 Duo 2GHz
processor, 1GB RAM, running a 32 bit Linux 2.6.37 kernel. The Java
Virtual Machine used was version 1.6.0-24. The database used was MySQL
x.x, running on ....

%----------------------------------------
% Number of Keywords
%----------------------------------------
\subsection{Number of Keywords}
To be able to study the impact of different number of keywords, we
built a keywords database with 10.000 most popular English
words. These 10.000 words come from:
http://www.mit.edu/~ecprice/wordlist.10000 All the experiments in this
part are done with 50.000 posts randomly downloaded from internet. The
idea is to get some heterogeneous length and type of post such that it
is realistic.  The experiment shown here consist on building the index
for different number of keywords from the 10.000 keywords database and
explore the time and space complexity for the building of the state
machine and the building of the index once the state machine is built.

@@

  \begin{figure}
    \begin{center}
      \includegraphics[width=\textwidth,height=!]{numkeywordstimecomplexbuildsm}
    \end{center}
    \caption{Time to build Aho-Corasick state machine as a function of
      the number of keywords. Time taken is shown in miliseconds on the
      y-axis and the number of keywords on the x-axis}
    \label{fig:numkeywordstimecomplexbuildsm}
  \end{figure}

\item \textbf{Index Construction:} 
  The time taken for a state machines to build an inverted index of our
  corpus was measured. The test was repeated using state machines
  constructed with a varying number of keywords and the results plotted
  in figure \ref{fig:numkeywordstimecomplexbuildindex}. According to
  \cite{RefWorks:103} which proves that the number of state transitions
  involved in processing an input string is independent of the number of
  keywords used to construct the state machine, we would not expect the
  time complexity to increase with the size of the keyword set. However,
  as can be seen in \ref{fig:numkeywordstimecomplexbuildindex}, the time
  to build the index increases logarithmically with the number of
  keywords. This is likely due to the fac that as the number of keywords
  increases, so does the size of the index and the number of database
  interacts required to store and update the index.

  \begin{figure}
    \begin{center}
      \includegraphics[width=\textwidth,height=!]{numkeywordstimecomplexbuildindex}
    \end{center}
    \caption{Time to build the inverted index as a function of the
      number of keywords. Time taken is shown in miliseconds on the
      y-axis and the number of keywords on the x-axis}
    \label{fig:numkeywordstimecomplexbuildindex}
  \end{figure}

@@

\subsubsection{Space Complexity}
As we would have expected it, the space used by the index in the
database is proportional to the number of words we are using. It also
means that our words have the same probability at the beginning or at
the end of our 12,000 words dictionnary. This result is reflected in
figure \ref{fig:numkeywordsspacecomplexbuildindex}.

@@

%----------------------------------------
% Size of Corpus
%----------------------------------------
\subsection{Size of Corpus}
To be able to study the impact of different number of Posts, we built
a posts database with 400.000 posts randomly downloaded from
internet. Then the keywords used to build the index are simply the
first 5.000 from the previous keywords database.

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{corpsizetimecomplexbuildindex}
  \end{center}
    \caption{Time to build the inverted index as a function of the
      size of the corpus. Time taken is shown in miliseconds on the
      y-axis and the number of documents in the collection on the
      x-axis} 
    \label{fig:corpsizetimecomplexbuildindex}
\end{figure}

\subsubsection{Space Complexity}
As expected, the space used to sptore the index in the database is
proportional to the size of the corpus. This result is shown in figure
\ref{fig:corpsizespacecomplexbuildindex}.

@@

%----------------------------------------
% Document Size
%----------------------------------------
\subsection{Document Size} 
As we have seen before, the time to build the index is almost
proportional with the number of post. Theoretically this time should
be proportional to the total length of all posts. Let’s focus on this
aspect and study the impact of the length of the post on the time to
build the state machine. To do that we built a 5.000 posts database
with posts that are all composed of 20.000 characters. Then, we ran
our system on different length of substring of these posts.

\subsubsection{Time Complexity}
\begin{itemize}
\item \textbf{State Machine Construction:} 
  As expected, state machine construction time
  does not depend on the length of the documents. Nonetheless it is
  interesting to compare figures \ref{fig:docsizetimecomplexbuildsm}
  and \ref{fig:docsizetimecomplexbuildindex}, showing the construction
  times for the state machine and inverted index relative to the
  average document size. The comparison shows that state machine
  construction time is several orders of magnitude smaller than index
  construction and negligible by comnparison. Our state machine is
  built in 770 ms on average for 1000 keywords with a standard
  deviation of 18ms.

  \begin{figure}
    \begin{center}
      \includegraphics[width=\textwidth,height=!]{docsizetimecomplexbuildsm}
    \end{center}
    \caption{Time to build Aho-Corasick state machine as a function of
      the average document size. Time taken is shown in miliseconds on the
      y-axis and the average document size in characters on the x-axis}
    \label{fig:docsizetimecomplexbuildsm}
  \end{figure}

@@

  \begin{figure}
    \begin{center}
      \includegraphics[width=\textwidth,height=!]{docsizetimecomplexbuildindex}
    \end{center}
    \caption{Time to build an inverted index as a function of the
      average document size. Time taken is shown in miliseconds on the
      y-axis and the average document size in characters on the x-axis} 
    \label{fig:docsizetimecomplexbuildindex}
  \end{figure}

@@

%----------------------------------------
% Comparison with Naive Index Builder
%----------------------------------------
\subsection{Comparison with Na\"{i}ve Index Builder}
This part focuses on the improvement that our system with respect to
time complexity in comparison with a na\"{i}e index builder. The na\"{i}ve
indexer builder has the same input as our system i.e. a list of
keywords and a list of documents, and the same output i.e. an inverted
index corresponding to the keywords and documents. Algorithm
\ref{alg:invertedindex} is used in principal for both implementations.

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{naivedocumentsizelog}
  \end{center}
  \caption{Time to build an inverted index as a function of the
      average document size. Time taken is shown in miliseconds on the
      y-axis and the average document size in characters on the
      logarithmic x-axis}
  \label{fig:naivedocumentsizelog}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{naivenumkeywords}
  \end{center}
  \caption{Time to build an inverted index as a function of the
      number of keywords. Time taken is shown in miliseconds on the
      y-axis and the number of keywords on the x-axis}
  \label{fig:naivenumkeywords}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{naivenumkeywordslog}
  \end{center}
  \caption{Time to build an inverted index as a function of the
      number of keywords. Time taken is shown in miliseconds on the
      y-axis and the number of keywords on the logarithmic x-axis}
  \label{fig:naivenumkeywordslog}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{naivesizecorpus}
  \end{center}
  \caption{Time to build an inverted index as a function of the
      number of documents being indexed. Time taken is shown in
      miliseconds on the y-axis and the number of documents on the
      x-axis} 
  \label{fig:naivesizecorpus}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{naivesizecorpuslog}
  \end{center}
  \caption{Time to build an inverted index as a function of the
      number of documents being indexed. Time taken is shown in
      miliseconds on the y-axis and the number of documents on the
      logarithmic x-axis} 
  \label{fig:naivesizecorpuslog}
\end{figure}

>>>>

Algorithm enhancements usually represent the forefront of research in
the field. Work to validate a new concept or algorithm is usually
performed in a very controlled environment and on relatively small
document collections. As the field matures, improvements are harder
fought and often involve increasingly complex algorithms and corpus
approximation methods into which it becomes more difficult to
\textit{fold-in} new documents. In addressing the considerable
computation cost of re-calculating \textit{Latent Semantic Indexing}
(LSI) \cite{RefWorks:102} approximations, \cite{RefWorks:101}
introduced new update methods which saw improved average precisions
but were forced to conclude that the improvements were at a
computational premium over previous methods. A semi-discrete matrix
decomposition for LSI, \textit{SDD}, performs as well as the original
SVD-based LSI method for equal query times and uses less storage
\cite{RefWorks:99}. The decomposition time of the new method, however,
is significantly larger than the original.

@@

%----------------------------------------
% Research Plan
%----------------------------------------
\section{Research Plan}
\label{sec:researchplan}
The primary goals of this research project is to construct an
information retrieval framework within which specific implementations
can be evaluated under various operating conditions. To initiate the
synthesis of this general framework, a reference implementation will
be built, based on the notion of a simple inverted index.

The software architecture of the reference implementation will be
carefully documented and follow established design patterns in order
to facilitate the future construction of alternative document search
schemes within the same framework. The framework will be designed to
be executed in a distributed deployment such that it may be used to
evaluate the effect of parallelization on a particular algorithm.

The performance of the reference implementation will be tested with
respect to the following operating parameters and compared to analytic
expectations:

\begin{itemize}
\item Number of index keywords
\item Number of documents in collection
\item Average size of documents
\end{itemize}

In addition, the reference implementation will be compared against a
na\"{i}ve implementation of the inverted indexer. The na\"{i}ve
implementation provided a baseline for further evaluation.

@@

\begin{figure}
  \begin{center}
        \includegraphics[angle=90,width=\textwidth,height=!]{overallclassdiagram}
  \end{center}
  \caption{Overall UML class diagram design}
  \label{fig:overallclassdiagram}
\end{figure}

@@

The indexer system maintains an \textit{inverted index} of an evolving
corpus and services concurrent search requests against the index. The
current implementation is based on boolean retrieval methods described
in \cite{RefWorks:109}. An Aho-Corasick state machine
\cite{RefWorks:103} is used to scan documents for a predefined set of
keywords, and construct a term index for each document (delta
index). The term occurrences for each document are used to augment an
existing index of documents already processed. The document
collection, index, and keyword list are maintained in a single MySQL
database instance. It is through this database that the parallel
indexer instances are initialized and synchronized. This configuration
is operationally simple and easy to implement but the database has the
potential to become a throttle point as the system is scaled to larger
and more rapidly evolving document collections, and is required to
service a higher rate of queries. In order to scale the current
implementation to large document collections, a more efficient
mechanism would be required in this respect.

@@

\begin{itemize}
\item \texttt{List<Document> getDocuments (int count)}: retrieve a
  specified number of unprocessed documents from the database. The
  documents retrieved will be atomically marked as processed so that
  processing is not duplicated on other nodes. In this scheme, a
  document is considered \textit{processed} once retrieved from the
  database. This may cause problems from a fault recovery perspective
  if the processing node fails. A proposed enhancement to this scheme
  is to use an intermediate state, \textit{processing}, to indicate
  that the document has been retrieved and to update the state to
  \textit{processed} once processing is actually complete. For the
  initial implementation we will use the \textit{processed} state
  only.

@@

 Figures \ref{fig:indexclassdiagram} and
 \ref{fig:indexsequencediagram} show UML class and sequence
 diagrams respectively for classes and methods involved in the
 implementation of the Index data access layer.

@@

Figures \ref{fig:searcherclassdiagram} and
\ref{fig:searchersequencediagram} show UML class and sequence
diagrams respectively for classes and methods involved in the
implementation of the \texttt{Searcher} class.

@@

Figures \ref{fig:statemachineclassdiagram} and
\ref{fig:statemachinesequencediagram} show UML class and sequence
diagrams respectively for classes and methods involved in the
implementation of the \texttt{StateMachineBuilder}.

@@

Figures \ref{fig:parserclassdiagram} and
\ref{fig:parsersequencediagram} show UML class and sequence
diagrams respectively for classes and methods involved in the
implementation of the \texttt{Parser}.

@@

%----------------------------------------
% Experiment Results
%----------------------------------------
\section{Experiment Results}
\label{sec:experimentresults}
The primary goal of this project is to be able to reduce the time
to build a document index. As our system is building the inverted index by
parsing all documents of the collection, we can expect the
time complexity of the task to be proportional to the sum total of
characters in the collection. As a result, changing the  
number of documents or the average size of each document should
have a big impact in our time complexity. In addition, our
implementation will incur the cost of building the Aho-Corasick state
machines used to scan the documents. We can expect the time to build a
state machine to be proportional to the sum of the size of the
keywords.

Finally we will do a time comparison between our indexer
implementation and a na\"{i}ve implementation. All the time
complexities tests are  
done on a single computer and it is important to understand that all
these processes can be parallelized. A future work would be to install
our indexer on multiple computers and explore the performance gain of
running parallel instances simultaneously on all these computers.

All tests were run on a single Intel Core 2 Duo 2GHz
processor, 1GB RAM, running a 64-bit Linux 2.6.35 SMP kernel. The Java
Virtual Machine used was version 1.6.0-24. The database used was
MySQL, running on the same node as the indexer.

%----------------------------------------
% Number of Keywords
%----------------------------------------
\subsection{Number of Keywords}
To be able to study the impact of different number of keywords, we
built a keywords database with 10,000 most popular English
words \cite{wordlist}. All the experiments in this
part are done with 50,000 posts randomly downloaded from the Internet. The
idea is to get a good distribution of documents with respect to length
and content. The experiment shown here consist of building the index
for different numbers of keywords from the 10,000 keyword database and
explore the time and space complexity for the building of the state
machine and the building of the index using the state machine.

@@

  \begin{figure}
    \begin{center}
      \includegraphics[width=\textwidth,height=!]{numkeywordstimecomplexbuildsm}
    \end{center}
    \caption{Time to build Aho-Corasick state machine as a function of
      the number of keywords. Time taken is shown in milliseconds on the
      y-axis and the number of keywords on the x-axis}
    \label{fig:numkeywordstimecomplexbuildsm}
  \end{figure}

\item \textbf{Index Construction:} 
  The time taken for a state machines to build an inverted index of our
  corpus was measured. The test was repeated using state machines
  constructed with a varying number of keywords and the results plotted
  in figure \ref{fig:numkeywordstimecomplexbuildindex}. According to
  \cite{RefWorks:103} which proves that the number of state transitions
  involved in processing an input string is independent of the number of
  keywords used to construct the state machine, we would not expect the
  time complexity to increase with the size of the keyword set. However,
  as can be seen in \ref{fig:numkeywordstimecomplexbuildindex}, the time
  to build the index increases logarithmically with the number of
  keywords. This is likely due to the fact that as the number of keywords
  increases, so does the size of the index and the number of database
  interacts required to store and update the index.

  \begin{figure}
    \begin{center}
      \includegraphics[width=\textwidth,height=!]{numkeywordstimecomplexbuildindex}
    \end{center}
    \caption{Time to build the inverted index as a function of the
      number of keywords. Time taken is shown in milliseconds on the
      y-axis and the number of keywords on the x-axis}
    \label{fig:numkeywordstimecomplexbuildindex}
  \end{figure}

@@

\subsubsection{Space Complexity}
As we would have expected it, the space used by the index in the
database is proportional to the number of words we are using. It also
means that our words have the same probability at the beginning or at
the end of our 12,000 word dictionary. This result is reflected in
figure \ref{fig:numkeywordsspacecomplexbuildindex}.

@@

%----------------------------------------
% Size of Corpus
%----------------------------------------
\subsection{Size of Corpus}
To be able to study the impact of different number of Posts, we built
a posts database with 400,000 posts randomly downloaded from
the Internet. Then the keywords used to build the index are simply the
first 5,000 from the previous keywords database.

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{corpsizetimecomplexbuildindex}
  \end{center}
    \caption{Time to build the inverted index as a function of the
      size of the corpus. Time taken is shown in milliseconds on the
      y-axis and the number of documents in the collection on the
      x-axis} 
    \label{fig:corpsizetimecomplexbuildindex}
\end{figure}

\subsubsection{Space Complexity}
As expected, the space used to store the index in the database is
proportional to the size of the corpus. This result is shown in figure
\ref{fig:corpsizespacecomplexbuildindex}.

@@

%----------------------------------------
% Document Size
%----------------------------------------
\subsection{Document Size} 
As we have seen before, the time to build the index is almost
proportional with the number of post. Theoretically this time should
be proportional to the total length of all posts. Let’s focus on this
aspect and study the impact of the length of the post on the time to
build the state machine. To do that we built a 5,000 posts database
with posts that are all composed of 20,000 characters. Then, we ran
our system on different length of substring of these posts.

\subsubsection{Time Complexity}
\begin{itemize}
\item \textbf{State Machine Construction:} 
  As expected, state machine construction time
  does not depend on the length of the documents. Nonetheless it is
  interesting to compare figures \ref{fig:docsizetimecomplexbuildsm}
  and \ref{fig:docsizetimecomplexbuildindex}, showing the construction
  times for the state machine and inverted index relative to the
  average document size. The comparison shows that state machine
  construction time is several orders of magnitude smaller than index
  construction and negligible by comparison. Our state machine is
  built in 770 ms on average for 1000 keywords with a standard
  deviation of 18ms.

  \begin{figure}
    \begin{center}
      \includegraphics[width=\textwidth,height=!]{docsizetimecomplexbuildsm}
    \end{center}
    \caption{Time to build Aho-Corasick state machine as a function of
      the average document size. Time taken is shown in milliseconds on the
      y-axis and the average document size in characters on the x-axis}
    \label{fig:docsizetimecomplexbuildsm}
  \end{figure}

@@

  \begin{figure}
    \begin{center}
      \includegraphics[width=\textwidth,height=!]{docsizetimecomplexbuildindex}
    \end{center}
    \caption{Time to build an inverted index as a function of the
      average document size. Time taken is shown in milliseconds on the
      y-axis and the average document size in characters on the x-axis} 
    \label{fig:docsizetimecomplexbuildindex}
  \end{figure}

@@

%----------------------------------------
% Comparison with Naive Index Builder
%----------------------------------------
\subsection{Comparison with Na\"{i}ve Index Builder}
This part focuses on the improvement that our system with respect to
time complexity in comparison with a na\"{i}ve index builder. The na\"{i}ve
indexer builder has the same input as our system i.e. a list of
keywords and a list of documents, and the same output i.e. an inverted
index corresponding to the keywords and documents. Algorithm
\ref{alg:invertedindex} is used in principal for both implementations.

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{naivedocumentsizelog}
  \end{center}
  \caption{Time to build an inverted index as a function of the
      average document size. Time taken is shown in milliseconds on the
      y-axis and the average document size in characters on the
      logarithmic x-axis}
  \label{fig:naivedocumentsizelog}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{naivenumkeywords}
  \end{center}
  \caption{Time to build an inverted index as a function of the
      number of keywords. Time taken is shown in milliseconds on the
      y-axis and the number of keywords on the x-axis}
  \label{fig:naivenumkeywords}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{naivenumkeywordslog}
  \end{center}
  \caption{Time to build an inverted index as a function of the
      number of keywords. Time taken is shown in milliseconds on the
      y-axis and the number of keywords on the logarithmic x-axis}
  \label{fig:naivenumkeywordslog}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{naivesizecorpus}
  \end{center}
  \caption{Time to build an inverted index as a function of the
      number of documents being indexed. Time taken is shown in
      milliseconds on the y-axis and the number of documents on the
      x-axis} 
  \label{fig:naivesizecorpus}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,height=!]{naivesizecorpuslog}
  \end{center}
  \caption{Time to build an inverted index as a function of the
      number of documents being indexed. Time taken is shown in
      milliseconds on the y-axis and the number of documents on the
      logarithmic x-axis} 
  \label{fig:naivesizecorpuslog}
\end{figure}
